Marlowe: financial contracts on blockchain

### 2018-05-17 tex/paper.tex
tidied up contributions; misc other updates

We make the following contributions in this paper.
\begin{itemize}
\item
The design of the Marlowe language as a Haskell data type; Marlowe is made more expressible through its embedding in Haskell.
\item
An executable, small-step semantics of Marlowe in Haskell.
\item
The Meadow tool that allows users to simulate the operation of Marlowe contracts, including ``embedded'' contracts that use features of Haskell. 
\end{itemize}

@@

The paper is structured like this: REWRITE we begin in Section \ref{section:design} with a discussion of the design rationale 
for Marlowe, including an overview of the various approaches to scripting in blockchain as well as the different designs 
of the blockchains themselves. We conclude Section \ref{section:design} with a set of decisions about the blockchain 
environment for Marlowe. The central part of the paper is Section \ref{section:model} where we introduce the Marlowe 
model, including the assumptions made in designing it, the types of the principal functions and a description of the DSL 
as an algebraic type, constructor by constructor. 
%Section \ref{section:example-saving} presents an example of a larger Marlowe contract, for incentivised saving. 
Section \ref{section:example-escrow} revisits the escrow example, and shows 
how it is described using a combination of Marlowe and Haskell constructs: that is, we use Marlowe as an embedded DSL. 
Section \ref{section:tool} introduces Meadow, our tool for visualising and interacting with Marlowe contracts.
Section \ref{section:reflection} reflects on the system design, and observes some alternative designs and Section 
\ref{section:next-steps} enumerates the next steps for the project.

@@

The \haskellinline{step} function represents a \emph{single computation step} and has this type:
\begin{haskellcode}
step :: Input -> State -> Contract -> OS -> (State,Contract,AS)
\end{haskellcode}
which is also illustrated in Figure \ref{fig:step-function}.

The \haskellinline{step} function is total, so that for every contract a result of stepping is defined. However, for 
some kinds of contracts -- commits, redeems or time-shifted contracts -- it is possible that the result of a step is to 
produce the same contract as the result; such a step is called \emph{quiescent} whereas all other steps \emph{make 
progress}. We use this distinction in the explanation that follows.

@@

\section{Marlowe as an embedded DSL in Haskell}
\label{section:example-escrow}

@@

The example contract we use through this section implements an escrow contract. Let us imagine that participant 
\haskellinline{1} is buying some item from participant \haskellinline{2}. On one hand, if participant \haskellinline{1} 
pays before receiving the item, there is a risk that participant \haskellinline{2} will never give \haskellinline{1} the 
item. On the other hand, if participant \haskellinline{2} gives participant \haskellinline{1} the item before 
\haskellinline{1} pays, then there is a risk that \haskellinline{1} will never pay.

@@

\section{Visualising and interacting with contracts}

>>>>

We make the following contributions in this paper.
\begin{itemize}
\item
The design of the Marlowe language.
\item
An executable, small-step semantics of Marlowe in Haskell.
\item 
Extending Marlowe's expressibility by embedding it as a Haskell \haskellinline{data} type.
\item
The Meadow tool that allows users to interact with and simulate the operation of embedded Marlowe contracts. 
\end{itemize}

@@

The paper begins in Section \ref{section:model} by introducing the Marlowe 
model, including the assumptions made in designing it, the types of the principal functions and a description of the DSL as an algebraic type, constructor by constructor. 
%Section \ref{section:example-saving} presents an example of a larger Marlowe contract, for incentivised saving. 
Section \ref{section:example-escrow} revisits the escrow example, and shows 
how it is described using a combination of Marlowe and Haskell constructs: that is, we use Marlowe as an embedded DSL. 
Section \ref{section:tool} introduces Meadow, our tool for visualising and interacting with Marlowe contracts.
Section \ref{section:reflection} reflects on the system design, and observes some alternative designs and Section 
\ref{section:next-steps} enumerates the next steps for the project.

we begin in Section \ref{section:design} with a discussion of the design rationale 
for Marlowe, including an overview of the various approaches to scripting in blockchain as well as the different designs 
of the blockchains themselves. We conclude Section \ref{section:design} with a set of decisions about the blockchain 
environment for Marlowe.

@@

The \haskellinline{step} function represents a \emph{single computation step} and has this type:
\begin{haskellcode}
step :: Input -> State -> Contract -> OS -> (State,Contract,AS)
\end{haskellcode}
which is also illustrated in Figure \ref{fig:step-function}. 
The \haskellinline{step} function is total, so that for every contract a result of stepping is defined. However, for 
some kinds of contracts -- commits, redeems or time-shifted contracts -- it is possible that performing  a step produces the same contract as the result; we call these \emph{quiescent} steps whereas all others \emph{make 
progress}. We use this distinction in the explanation that follows.

@@

\section{Marlowe as an embedded DSL}
\label{section:example-escrow}

@@

The example contract we use through this section implements an escrow contract. Let us imagine that participant 
\haskellinline{1} is buying some item from participant \haskellinline{2}. On one hand, if participant \haskellinline{1} 
pays before receiving the item, there is a risk that participant \haskellinline{2} will never give \haskellinline{1} the 
item. On the other hand, if participant \haskellinline{2} gives participant \haskellinline{1} the item before 
\haskellinline{1} pays,  there is a risk that \haskellinline{1} will never pay.

@@

\section{Visualising and interacting with Marlowe contracts}
